
---
title: "NBA PERFORMANCE ANALYSIS PROJECT"
author: "David Rafanan and Cory Dickson"
date: "December 15, 2016"
output:
html_document: default
---
###AFTER INSTALLING THE PACKAGE DO NOT CONNECT TO TWITTER TO RETRIEVE THE TWEETS INSTEAD START THE CODE FROM READRDS
```{r} 
install.packages('lsa')
install.packages('twitteR')
install.packages('tm')
install.packages('ngram')
install.packages('plyr')
install.packages('stylo')
install.packages('wordcloud')
install.packages("SnowballC")
install.packages('lubridate')
install.packages('ggplot2')
library(lsa)
library(SnowballC)
library(wordcloud)
library(ngram)
library(plyr)
library(stylo)
library(twitteR)
library(tm)
library(lubridate)
library(ggplot2)
```

#Twitter Authentication
```{r}
lapply(c('twitteR', 'ggplot2', 'lubridate', 'tm'), library, character.only = TRUE)
theme_set(new = theme_bw())
source('../../R/twitterAuth.R')
set.seed(9561)
key <- 'jPEdMwCjSY01HmGCTFc9IaTik'
secret <- 'mkO1Dz9fv5MpmQhDPGBxzzgwV96tHUoCkxazs4TY501OrNuvfv'
access_token <- '805992778031366144-pMoJ8a4cWPI1VldJ6ZUk2RQ8r7Ztvla'
access_secret <- 'dguZ2IxpPi3BJIagx0T58SkN5sS6dQS00D1nVZMoYd9BZ'
options(tz="America/New York")
setup_twitter_oauth(key, secret, access_token, access_secret)
```

##Retrieve the tweets during the game -DO NOT RUN!!!!! LOAD FROM RDS!!!!! 
```{r}
twLJ = searchTwitter('Los Angeles Lakers', n = 3000, since = '2016-12-05', until = '2016-12-06')
twLM = searchTwitter('Los Angeles Lakers', n = 3000, since = '2016-12-03', until = '2016-12-04')
twLB = searchTwitter('Los Angeles Lakers', n = 3000, since = '2016-11-30', until = '2016-12-01')
twLS = searchTwitter('Los Angeles Lakers', n = 3000, since = '2016-12-09', until = '2016-12-10')
twLK = searchTwitter('Los Angeles Lakers', n = 1000, since = '2016-12-11', until = '2016-12-12')

##OKLAHOMA CITY THUNDER TWEETS #OKCThunder
twOP = searchTwitter('OKCThunder', n = 3000, since = '2016-12-13', until = '2016-12-14')
twOC = searchTwitter('OKCThunder', n = 3000, since = '2016-12-11', until = '2016-12-12')

#save a copy as backup # DO NOT RUN LOAD FROM RDS
saveRDS(twLJ, './NBA_TweetsLakersJazz.RDS')
saveRDS(twLM, './NBA_TweetsLakersMemphis.RDS')
saveRDS(twLB, './NBA_TweetsLakersBulls.RDS')
saveRDS(twLS, './NBA_TweetsLakersSuns.RDS')
saveRDS(twLK, './NBA_TweetsLakersKnicks.RDS')

#oklahoma
saveRDS(twOP, './NBA_TweetsThunderPortland.RDS')
saveRDS(twOC, './NBA_TweetsThunderCeltics.RDS')
```


##START THE CODE HERE#loading from file ###START OUR CODE HERE
```{r}
twLJ = readRDS('./NBA_TweetsLakersJazz.RDS')
twLM = readRDS('./NBA_TweetsLakersJazz.RDS')
twLB = readRDS('./NBA_TweetsLakersBulls.RDS')
twLS = readRDS('./NBA_TweetsLakersSuns.RDS')
twLK = readRDS('./NBA_TweetsLakersKnicks.RDS')

twOP = readRDS('./NBA_TweetsThunderPortland.RDS')
twOC = readRDS('./NBA_TweetsThunderCeltics.RDS')
```

#Convert to our timezone and refine the filter to the tweets during the game start and end time 
```{r}
#LakersVJazz Starttime: 7:30pm
LakersJazz = twListToDF(twLJ)
options(tz="America/New York")
LakersJazz$created <- with_tz(LakersJazz$created, 'America/New York')
LiveTweetsLakersJazz<- subset(LakersJazz, format(LakersJazz$created, "%H:%M:$S") > "19:30:00" & format(LakersJazz$created, "%H:%M:$S") < "22:45:00")

#LakersVMemphisGrizzly's Starttime: 8:00pm
LakersMemphis = twListToDF(twLM)
options(tz="America/New York")
LakersMemphis$created <- with_tz(LakersMemphis$created, 'America/New York')
LiveTweetsLakersMemphis<- subset(LakersMemphis, format(LakersMemphis$created, "%H:%M:$S") > "20:00:00" & format(LakersMemphis$created, "%H:%M:$S") < "23:00:00")

#LakersVChicagoBulls Starttime: 8:00pm
LakersBulls = twListToDF(twLB)
options(tz="America/New York")
LakersBulls$created <- with_tz(LakersBulls$created, 'America/New York')
LiveTweetsLakersBulls <- subset(LakersBulls, format(LakersBulls$created, "%H:%M:$S") > "20:00:00" & format(LakersBulls$created, "%H:%M:$S") < "23:00:00")

#LakersVPheonixSuns Starttime: 10:30pm
LakersSuns = twListToDF(twLS)
options(tz="America/New York")
LakersSuns$created <- with_tz(LakersSuns$created, 'America/New York')
LiveTweetsLakersSuns <- subset(LakersSuns, format(LakersSuns$created, "%H:%M:$S") > "21:30:00" & format(LakersSuns$created, "%H:%M:$S") < "24:00:00")

#LakersVNewYorkKnicks Starttime: 10:30pm
LakersKnicks = twListToDF(twLK)
options(tz="America/New York")
LakersKnicks$created <- with_tz(LakersKnicks$created, 'America/New York')
LiveTweetsLakersKnicks <- subset(LakersKnicks, format(LakersKnicks$created, "%H:%M:$S") > "21:00:00" & format(LakersKnicks$created, "%H:%M:$S") < "24:00:00")

#OklahomaVPortland Starttime: 10:30pm
ThunderPort = twListToDF(twOP)
ThunderPort$created <- with_tz(ThunderPort$created, 'America/New York')
LiveTweetsThunderPort<- subset(ThunderPort, format(ThunderPort$created, "%H:%M:$S") > "22:30:00" & format(ThunderPort$created, "%H:%M:$S") < "24:00:00")

#OklahomaVCeltics Starttime: 7:00pm
ThunderCeltics = twListToDF(twOC)
ThunderCeltics$created <- with_tz(ThunderCeltics$created, 'America/New York')
LiveTweetsThunderCeltics<- subset(ThunderCeltics, format(ThunderCeltics$created, "%H:%M:$S") > "19:00:00" & format(ThunderCeltics$created, "%H:%M:$S") < "22:30:00")
```

#Remove emoji's and other unknown characters from the dataset
```{r}
LiveTweetsLakersSuns$text <- sapply(LiveTweetsLakersSuns$text,function(row) iconv(row, "utf-8-mac", "ASCII", sub=""))
LiveTweetsLakersBulls$text <- sapply(LiveTweetsLakersBulls$text,function(row) iconv(row, "utf-8-mac", "ASCII", sub=""))
LiveTweetsLakersMemphis$text <- sapply(LiveTweetsLakersMemphis$text,function(row) iconv(row, "utf-8-mac", "ASCII", sub=""))
LiveTweetsLakersJazz$text <- sapply(LiveTweetsLakersJazz$text,function(row) iconv(row, "utf-8-mac", "ASCII", sub=""))
LiveTweetsLakersKnicks$text <- sapply(LiveTweetsLakersKnicks$text,function(row) iconv(row, "utf-8-mac", "ASCII", sub=""))

LiveTweetsThunderPort$text<- sapply(LiveTweetsThunderPort$text,function(row) iconv(row, "utf-8-mac", "ASCII", sub=""))
LiveTweetsThunderCeltics$text<- sapply(LiveTweetsThunderCeltics$text,function(row) iconv(row, "utf-8-mac", "ASCII", sub=""))
```

# Make all the tweets lower case to make n-grams analysis easier
```{r}
LiveTweetsLakersSuns$text <-sapply(LiveTweetsLakersSuns$text, tolower)
LiveTweetsLakersBulls$text <-sapply(LiveTweetsLakersBulls$text, tolower)
LiveTweetsLakersMemphis$text <-sapply(LiveTweetsLakersMemphis$text, tolower)
LiveTweetsLakersJazz$text <-sapply(LiveTweetsLakersJazz$text, tolower)
LiveTweetsLakersKnicks$text <-sapply(LiveTweetsLakersKnicks$text, tolower)

LiveTweetsThunderPort$text <- sapply(LiveTweetsThunderPort$text, tolower)
LiveTweetsThunderCeltics$text <- sapply(LiveTweetsThunderCeltics$text, tolower)
```

#setting up corpus for good and bad basketball terms
```{r}
goodBasketballTerms= read.table("Good basketball terms.txt")
goodBasketballVector= VectorSource(goodBasketballTerms)
goodBasketballCorpus= Corpus(goodBasketballVector)

badBasketballTerms= read.table("Bad basketball terms.txt")
badBasketballVector= VectorSource(badBasketballTerms)
badBasketballCorpus= Corpus(badBasketballVector)
```

#regex expressions removing hash tags user ids, retweets and link headers to better denoise the data
```{r}
clean_tweets <- function(twitterList) {
  clean_tweet$text <- gsub("&amp", "", twitterList$text)
  clean_tweet$text <- gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", clean_tweet$text)
  clean_tweet$text <- gsub("@\\w+", "", clean_tweet$text)
  clean_tweet$text <- gsub("[[:punct:]]", "", clean_tweet$text)
  clean_tweet$text <- gsub("[[:digit:]]", "", clean_tweet$text)
  clean_tweet$text <- gsub("http\\w+", "", clean_tweet$text)
  clean_tweet$text <- gsub("[ \t]{2,}", "", clean_tweet$text)
  clean_tweet$text <- gsub("^\\s+|\\s+$", "", clean_tweet$text) 
  return(clean_tweet)
}

sanitizedLakersJazz <-clean_tweets(LiveTweetsLakersJazz)
sanitizedLakersBulls <-clean_tweets(LiveTweetsLakersBulls)
sanitizedLakersMemphis <-clean_tweets(LiveTweetsLakersMemphis)
sanitizedLakersSuns <-clean_tweets(LiveTweetsLakersSuns)
sanitizedLakersKnicks <-clean_tweets(LiveTweetsLakersKnicks)
sanitizedThunderPortland <-clean_tweets(LiveTweetsThunderPort)
sanitizedThunderCeltics <- clean_tweets(LiveTweetsThunderCeltics)
```


# Vizualization of the tweets via wordclouds
# Create corpus for each of the five games 
```{r}
corpusLJ =Corpus(VectorSource(sanitizedLakersJazz))
corpusLS =Corpus(VectorSource(sanitizedLakersSuns))
corpusLB =Corpus(VectorSource(sanitizedLakersBulls))
corpusLM =Corpus(VectorSource(sanitizedLakersMemphis))
corpusLK =Corpus(VectorSource(sanitizedLakersKnicks))

corpusTP =Corpus(VectorSource(sanitizedThunderPortland))
corpusTC =Corpus(VectorSource(sanitizedThunderCeltics))
```

# Remove stopwords such as: the, is, at, which, and on. This is to increase performance of our process.
```{r}
corpusLJ=tm_map(corpusLJ,function(x) removeWords(x,stopwords("english")))
corpusLS=tm_map(corpusLS,function(x) removeWords(x,stopwords("english")))
corpusLB=tm_map(corpusLB,function(x) removeWords(x,stopwords("english")))
corpusLM=tm_map(corpusLM,function(x) removeWords(x,stopwords("english")))
corpusLK=tm_map(corpusLK,function(x) removeWords(x,stopwords("english")))

corpusTP=tm_map(corpusTP,function(x) removeWords(x,stopwords("english")))
corpusTC=tm_map(corpusTC,function(x) removeWords(x,stopwords("english")))
```

# convert corpus to a Plain Text Document so we can vizualize using wordcloud
```{r}
corpusLJ=tm_map(corpusLJ,PlainTextDocument)

#display settings
par(mfrow=c(1,1))
col=brewer.pal(6,"Dark2")
```
#Word Clouds
```{r}
#Wordcloud: LakersVJazz
set.seed(2245)
wordcloud(corpusLJ, min.freq=25,rot.per = 0.35, random.color=F, max.word=45, random.order=F,colors=col)

#Wordcloud: LakersBulls
set.seed(1550)
corpusLB=tm_map(corpusLB,PlainTextDocument)
wordcloud(corpusLB, min.freq=25,rot.per = 0.35, random.color=F, max.word=45, random.order=F,colors=col)

#Wordcloud: LakersSuns
set.seed(3211)
corpusLS=tm_map(corpusLS,PlainTextDocument)
wordcloud(corpusLS, min.freq=25,rot.per = 0.35, random.color=F, max.word=45, random.order=F,colors=col)

#Wordcloud: LakersMemphis
set.seed(2111)
corpusLM=tm_map(corpusLM,PlainTextDocument)
wordcloud(corpusLM, min.freq=25,rot.per = 0.35, random.color=F, max.word=45, random.order=F,colors=col)

#Wordcloud: LakersKnicks
set.seed(4241)
corpusLK=tm_map(corpusLK,PlainTextDocument)
wordcloud(corpusLK, min.freq=25,rot.per = 0.35, random.color=F, max.word=45, random.order=F,colors=col)

#Oklahoma Port
set.seed(4211)
corpusTP=tm_map(corpusTP,PlainTextDocument)
wordcloud(corpusTP, min.freq=25,rot.per = 0.35, random.color=F, max.word=45, random.order=F,colors=col)

#Oklahoma Celtics
set.seed(3011)
corpusTC=tm_map(corpusTC,PlainTextDocument)
wordcloud(corpusTC, min.freq=25,rot.per = 0.35, random.color=F, max.word=45, random.order=F,colors=col)
```

#Create a frequency table of terms used in tweets
```{r}
dtmLakersJazz<- TermDocumentMatrix(corpusLJ)
m <- as.matrix(dtmLakersJazz)
v <- sort(rowSums(m),decreasing=TRUE)
freqTermsLakersJazz <- data.frame(word = names(v),freq=v)
head(freqTermsLakersJazz, 20)

dtmLakersMemphis<- TermDocumentMatrix(corpusLM)
m <- as.matrix(dtmLakersJazz)
v <- sort(rowSums(m),decreasing=TRUE)
freqTermsLakersMemphis <- data.frame(word = names(v),freq=v)
head(freqTermsLakersMemphis, 20)

dtmLakersBulls<- TermDocumentMatrix(corpusLB)
m <- as.matrix(dtmLakersBulls)
v <- sort(rowSums(m),decreasing=TRUE)
freqTermsLakersBulls <- data.frame(word = names(v),freq=v)
head(freqTermsLakersBulls, 20)

dtmLakersSuns<- TermDocumentMatrix(corpusLS)
m <- as.matrix(dtmLakersSuns)
v <- sort(rowSums(m),decreasing=TRUE)
freqTermsLakersSuns <- data.frame(word = names(v),freq=v)
head(freqTermsLakersSuns, 20)

dtmLakersKnicks<- TermDocumentMatrix(corpusLK)
m <- as.matrix(dtmLakersKnicks)
v <- sort(rowSums(m),decreasing=TRUE)
freqTermsLakersKnicks <- data.frame(word = names(v),freq=v)
head(freqTermsLakersKnicks, 20)


dtmThunderPort<- TermDocumentMatrix(corpusTP)
m <- as.matrix(dtmThunderPort)
v <- sort(rowSums(m),decreasing=TRUE)
freqTermsThunderPort <- data.frame(word = names(v),freq=v)
head(freqTermsThunderPort, 20)

dtmThunderCeltics<- TermDocumentMatrix(corpusTC)
m <- as.matrix(dtmThunderCeltics)
v <- sort(rowSums(m),decreasing=TRUE)
freqTermsThunderCeltics <- data.frame(word = names(v),freq=v)
head(freqTermsThunderCeltics, 20)
```



#file for player statistics
```{r}
PlayerStats<-read.csv("PlayerStats.csv")
```

#data frame ngrams for Lakers Jazz and showing most frequent terms 
```{r}
tblUnigramLakersJazz <- data.frame(table(make.ngrams(freqTermsLakersJazz, ngram.size = 1)))
tblBigramLakersJazz <- data.frame(table(make.ngrams(freqTermsLakersJazz, ngram.size = 2)))
tblTrigramLakersJazz <- data.frame(table(make.ngrams(freqTermsLakersJazz, ngram.size = 3)))


topTermsLakersJazzUnigram <- tblUnigramLakersJazz.unigram[1:20,]
colnames(topTermsLakersJazzUnigram) <- c("Lakers-Jazz Unigram", "Frequency")
topTermsLakersJazzBigram <- tblBigramLakersJazz.bigram[1:20,]
colnames(topTermsLakersJazzBigram) <- c("Lakers-Jazz Bigram", "Frequency")
topTermsLakersJazzTrigram <- tblTrigramLakersJazz.trigram[1:20,]
colnames(topTermsLakersJazzTrigram) <- c("Lakers-Jazz Trigram", "Frequency")

#plots
ggplot(topTermsLakersJazzUnigram, aes(x = reorder(Unigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Jazz Unigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersJazzBigram, aes(x = reorder(Bigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Jazz Bigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersJazzTrigram, aes(x = reorder(Trigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Jazz Trigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#data frame ngrams for Lakers Memphis
tblUnigramLakersMemphis <- data.frame(table(make.ngrams(freqTermsLakersMemphis, ngram.size = 1)))
tblBigramLakersMemphis <- data.frame(table(make.ngrams(freqTermsLakersMemphis, ngram.size = 2)))
tblTrigramLakersMemphis <- data.frame(table(make.ngrams(freqTermsLakersMemphis, ngram.size = 3)))


topTermsLakersMemphisUnigram <- tblUnigramLakersMemphis.unigram[1:20,]
colnames(topTermsLakersMemphisUnigram) <- c("Lakers-Memphis Unigram", "Frequency")
topTermsLakersMemphisBigram <- tblBigramLakersMemphis.bigram[1:20,]
colnames(topTermsLakersMemphisBigram) <- c("Lakers-Memphis Bigram", "Frequency")
topTermsLakersMemphisTrigram <- tblTrigramLakersMemphis.trigram[1:20,]
colnames(topTermsLakersMemphisTrigram) <- c("Lakers-Memphis Trigram", "Frequency")


#plots
ggplot(topTermsLakersMemphisUnigram, aes(x = reorder(Unigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Memphis Unigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersMemphisBigram, aes(x = reorder(Bigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Memphis Bigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersMemphisTrigram, aes(x = reorder(Trigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Memphis Trigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#data frame ngrams for Lakers Bulls
tblUnigramLakersBulls <- data.frame(table(make.ngrams(freqTermsLakersBulls, ngram.size = 1)))
tblBigramLakersBulls <- data.frame(table(make.ngrams(freqTermsLakersBulls, ngram.size = 2)))
tblTrigramLakersBulls <- data.frame(table(make.ngrams(freqTermsLakersBulls, ngram.size = 3)))


topTermsLakersBullsUnigram <- tblUnigramLakersBulls.unigram[1:20,]
colnames(topTermsLakersBullsUnigram) <- c("Lakers-Bulls Unigram", "Frequency")
topTermsLakersBullsBigram <- tblBigramLakersBulls.bigram[1:20,]
colnames(topTermsLakersBullsBigram) <- c("Lakers-Bulls Bigram", "Frequency")
topTermsLakersBullsTrigram <- tblTrigramLakersBulls.trigram[1:20,]
colnames(topTermsLakersBullsTrigram) <- c("Lakers-Bulls Trigram", "Frequency")


#plots
ggplot(topTermsLakersBullsUnigram, aes(x = reorder(Unigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Bulls Unigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersBullsBigram, aes(x = reorder(Bigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Bulls Bigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersBullsTrigram, aes(x = reorder(Trigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Bulls Trigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#data frame ngrams for Lakers Suns
tblUnigramLakersSuns <- data.frame(table(make.ngrams(freqTermsLakersSuns, ngram.size = 1)))
tblBigramLakersSuns <- data.frame(table(make.ngrams(freqTermsLakersSuns, ngram.size = 2)))
tblTrigramLakersSuns <- data.frame(table(make.ngrams(freqTermsLakersSuns, ngram.size = 3)))


topTermsLakersSunsUnigram <- tblUnigramLakersSuns.unigram[1:20,]
colnames(topTermsLakersSunsUnigram) <- c("Lakers-Suns Unigram", "Frequency")
topTermsLakersSunsBigram <- tblBigramLakersSuns.bigram[1:20,]
colnames(topTermsLakersSunsBigram) <- c("Lakers-Suns Bigram", "Frequency")
topTermsLakersSunsTrigram <- tblTrigramLakersSuns.trigram[1:20,]
colnames(topTermsLakersSunsTrigram) <- c("Lakers-Suns Trigram", "Frequency")


#plots
ggplot(topTermsLakersSunsUnigram, aes(x = reorder(Unigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Suns Unigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersSunsBigram, aes(x = reorder(Bigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Suns Bigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersSunsTrigram, aes(x = reorder(Trigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Suns Trigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#data frame ngrams for Lakers Knicks
tblUnigramLakersKnicks <- data.frame(table(make.ngrams(freqTermsLakersKnicks, ngram.size = 1)))
tblBigramLakersKnicks <- data.frame(table(make.ngrams(freqTermsLakersKnicks, ngram.size = 2)))
tblTrigramLakersKnicks <- data.frame(table(make.ngrams(freqTermsLakersKnicks, ngram.size = 3)))


topTermsLakersKnicksUnigram <- tblUnigramLakersKnicks.unigram[1:20,]
colnames(topTermsLakersKnicksUnigram) <- c("Lakers-Knicks Unigram", "Frequency")
topTermsLakersKnicksBigram <- tblBigramLakersKnicks.bigram[1:20,]
colnames(topTermsLakersKnicksBigram) <- c("Lakers-Knicks Bigram", "Frequency")
topTermsLakersKnicksTrigram <- tblTrigramLakersKnicks.trigram[1:20,]
colnames(topTermsLakersKnicksTrigram) <- c("Lakers-Knicks Trigram", "Frequency")


#plots
ggplot(topTermsLakersKnicksUnigram, aes(x = reorder(Unigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Knicks Unigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersKnicksBigram, aes(x = reorder(Bigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Knicks Bigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsLakersKnicksTrigram, aes(x = reorder(Trigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Lakers Knicks Trigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#data frame ngrams for Thunder Trailblazers
tblUnigramThunderPort <- data.frame(table(make.ngrams(freqTermsThunderPort, ngram.size = 1)))
tblBigramThunderPort <- data.frame(table(make.ngrams(freqTermsThunderPort, ngram.size = 2)))
tblTrigramThunderPort <- data.frame(table(make.ngrams(freqTermsThunderPort, ngram.size = 3)))


topTermsThunderPortUnigram <- tblUnigramThunderPort.unigram[1:20,]
colnames(topTermsThunderPortUnigram) <- c("Thunder-Portland Unigram", "Frequency")
topTermsThunderPortBigram <- tblBigramThunderPort.bigram[1:20,]
colnames(topTermsThunderPortBigram) <- c("Thunder-Port Bigram", "Frequency")
topTermsThunderPortTrigram <- tblTrigramThunderPort.trigram[1:20,]
colnames(topTermsThunderPortTrigram) <- c("Thunder-Port Trigram", "Frequency")


#plots
ggplot(topTermsThunderPortUnigram, aes(x = reorder(Unigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Thunder Portland Unigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsThunderPortBigram, aes(x = reorder(Bigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Thunder Portland Bigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsThunderPortTrigram, aes(x = reorder(Trigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Thunder Portland Trigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#data frame ngrams for Thunder Celtics
tblUnigramThunderCeltics <- data.frame(table(make.ngrams(freqTermsThunderCeltics, ngram.size = 1)))
tblBigramThunderCeltics <- data.frame(table(make.ngrams(freqTermsThunderCeltics, ngram.size = 2)))
tblTrigramThunderCeltics <- data.frame(table(make.ngrams(freqTermsThunderCeltics, ngram.size = 3)))


topTermsThunderCelticsUnigram <- tblUnigramThunderCeltics.unigram[1:20,]
colnames(topTermsThunderCelticsUnigram) <- c("Thunder-Celtics Unigram", "Frequency")
topTermsThunderCelticsBigram <- tblBigramThunderCeltics.bigram[1:20,]
colnames(topTermsThunderCelticsBigram) <- c("Thunder-Celtics Bigram", "Frequency")
topTermsThunderCelticsTrigram <- tblTrigramThunderCeltics.trigram[1:20,]
colnames(topTermsThunderCelticsTrigram) <- c("Thunder-Celtics Trigram", "Frequency")


#plots
ggplot(topTermsThunderCelticsUnigram, aes(x = reorder(Unigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Thunder Celtics Unigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsThunderCelticsBigram, aes(x = reorder(Bigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Thunder Celtics Bigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(topTermsThunderCelticsTrigram, aes(x = reorder(Trigram, - Frequency), y = Frequency)) + 
  geom_bar(stat = "Identity", fill = "Black") +  
  geom_text(aes(label = Frequency), vjust = - 0.20, size = 3) +
  xlab("Thunder Celtics Trigrams") +
  ylab("Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


#sentiment analysis
```{r}
basketball_sentiment_performance_Jazz = function(corpusLJ, goodBasketballCorpus, badBasketballCorpus, .progress='none' ) {
  
  LakersJazzScores = laply(corpusLJ, function(freqTermsLakersJazz,goodBasketballCorpus,badBasketballCorpus) {
  positive_matches = match(freqTermsLakersJazz,goodBasketballCorpus)
  negative_matches = match(freqTermsLakersJazz,badBasketballCorpus)
  positive_matches = !is.na(positive_matches)
  negative_matches = !is.na(negative_matches)
  score = sum(positive_matches) - sum(negative_matches)
  return(score)
  }, positive_matches, negative_matches, .progress=.progress)
  score_LakersJazz_df = data.frame(score=LakersJazzScores, text=freqTermsLakersJazz)
  return(score_LakersJazz_df)
}


basketball_sentiment_performance_Memphis = function(corpusLM, goodBasketballCorpus, badBasketballCorpus, .progress='none' ) {
  
LakersMemphisScores = laply(corpusLM, function(freqTermsLakersMemphis,goodBasketballCorpus,badBasketballCorpus) {
  positive_matches = match(freqTermsLakersMemphis,goodBasketballCorpus)
  negative_matches = match(freqTermsLakersMemphis,badBasketballCorpus)
  positive_matches = !is.na(positive_matches)
  negative_matches = !is.na(negative_matches)
  score = sum(positive_matches) - sum(negative_matches)
  return(score)
  }, positive_matches, negative_matches, .progress=.progress)
  score_LakersMemphis_df = data.frame(score=LakersMemphisScores, text=freqTermsLakersMemphis)
  return(score_LakersMemphis_df)
}


basketball_sentiment_performance_Bulls = function(corpusLB, goodBasketballCorpus, badBasketballCorpus, .progress='none' ) {
  
LakersBullsScores = laply(corpusLB, function(freqTermsLakersBulls,goodBasketballCorpus,badBasketballCorpus) {
  positive_matches = match(freqTermsLakersBulls,goodBasketballCorpus)
  negative_matches = match(freqTermsLakersBulls,badBasketballCorpus)
  positive_matches = !is.na(positive_matches)
  negative_matches = !is.na(negative_matches)
  score = sum(positive_matches) - sum(negative_matches)
  return(score)
  }, positive_matches, negative_matches, .progress=.progress)
  score_LakersBulls_df = data.frame(score=LakersBullsScores, text=freqTermsLakersBulls)
  return(score_LakersBulls_df)
}


basketball_sentiment_performance_Suns = function(corpusLS, goodBasketballCorpus, badBasketballCorpus, .progress='none' ) {
  
LakersSunsScores = laply(corpusLS, function(freqTermsLakersSuns,goodBasketballCorpus,badBasketballCorpus) {
  positive_matches = match(freqTermsLakersSuns,goodBasketballCorpus)
  negative_matches = match(freqTermsLakersSuns,badBasketballCorpus)
  positive_matches = !is.na(positive_matches)
  negative_matches = !is.na(negative_matches)
  score = sum(positive_matches) - sum(negative_matches)
  return(score)
  }, positive_matches, negative_matches, .progress=.progress)
  score_LakersBulls_df = data.frame(score=LakersSunsScores, text=freqTermsLakersSuns)
  return(score_LakersSuns_df)
}


basketball_sentiment_performance_Knicks = function(corpusLK, goodBasketballCorpus, badBasketballCorpus, .progress='none' ) {
  
LakersKnicksScores = laply(corpusLK, function(freqTermsLakersKnicks,goodBasketballCorpus,badBasketballCorpus) {
  positive_matches = match(freqTermsLakersKnicks,goodBasketballCorpus)
  negative_matches = match(freqTermsLakersKnicks,badBasketballCorpus)
  positive_matches = !is.na(positive_matches)
  negative_matches = !is.na(negative_matches)
  score = sum(positive_matches) - sum(negative_matches)
  return(score)
  }, positive_matches, negative_matches, .progress=.progress)
  score_LakersBulls_df = data.frame(score=LakersKnicksScores, text=freqTermsLakersKnicks)
  return(score_LakersKnicks_df)
}


basketball_sentiment_performance_ThunderPort = function(corpusTP, goodBasketballCorpus, badBasketballCorpus, .progress='none' ) {
  
ThunderPortScores = laply(corpusTP, function(freqTermsThunderPort,goodBasketballCorpus,badBasketballCorpus) {
  positive_matches = match(freqTermsThunderPort,goodBasketballCorpus)
  negative_matches = match(freqTermsThunderPort,badBasketballCorpus)
  positive_matches = !is.na(positive_matches)
  negative_matches = !is.na(negative_matches)
  score = sum(positive_matches) - sum(negative_matches)
  return(score)
  }, positive_matches, negative_matches, .progress=.progress)
  score_ThunderPort_df = data.frame(score=ThunderPortScores, text=freqTermsThunderPort)
  return(score_ThunderPort_df)
}


basketball_sentiment_performance_ThunderCeltics = function(corpusTC, goodBasketballCorpus, badBasketballCorpus, .progress='none' ) {
  
ThunderCelticsScores = laply(corpusTC, function(freqTermsThunderCeltics,goodBasketballCorpus,badBasketballCorpus) {
  positive_matches = match(freqTermsThunderCeltics,goodBasketballCorpus)
  negative_matches = match(freqTermsThunderCeltics,badBasketballCorpus)
  positive_matches = !is.na(positive_matches)
  negative_matches = !is.na(negative_matches)
  score = sum(positive_matches) - sum(negative_matches)
  return(score)
  }, positive_matches, negative_matches, .progress=.progress)
  score_ThunderCeltics_df = data.frame(score=ThunderCelticsScores, text=freqTermsThunderCeltics)
  return(score_ThunderCeltics_df)
}
```